Make any stupid plot you want

### 2021-02-14 draft/sections/next.tex
not totally coherant, halfway through what did we do list

\subsection{What have we done}
This work contributes a mathematical description of the transformation from data to visual representation. Combining Butler's fiber bundle model of data with Spivaks formalism of data schemas provides a way of decoupling topology from variability such that the model can support a very large variety of datasets, including discrete relational tables, multivariate high resolution spatio temporal datasets, and complex networks. Modeling the graphic as a fiber bundle provides a way to seperate the target display space from the topology of the graphic. By decomposing the mapping from data to visual representation as encoding \vchannel, assembly \vmark, and a mapping between data and graphic topologies \vindex and formalizing what equivariance each stage needs to preserved, we can derive constraints that visualization library authors could embed in their code to guaranteee visualizations that are equivariant transforms of the input data. While Mackinlay defined the visual encodings as equivariant maps, a new contribution is the generalization of topology preservation as an equivariant map from graphic space to data space.

>>>>

\subsection{What have we done}
This work contributes a mathematical description of the transformation from data to visual representation. Combining Butler's fiber bundle model of data with Spivaks formalism of data schemas provides a way of decoupling topology from variability such that the model can support a very large variety of datasets, including discrete relational tables, multivariate high resolution spatio temporal datasets, and complex networks. Modeling the graphic as a fiber bundle provides a way to seperate the target display space from the topology of the graphic. By decomposing the mapping from data to visual representation as encoding \vchannel, assembly \vmark, and a mapping between data and graphic topologies \vindex and formalizing what equivariance each stage needs to preserved, we can derive constraints that visualization library authors could embed in their code to guaranteee visualizations that are equivariant transforms of the input data. While Mackinlay discussed constraining visual encodings as equivariant maps, a new contribution is the generalization of topology preservation as a deformation retraction from graphic space to data space. By using a functional paradigm, we can deconstruct the graphic to the glyph associated with each data point or even to pieces of a glyph; therefore the renderer has full  flexibility in how to to generate the image, while the graphic to data topology maps provide a book keeping mechanism to keep track of which part of the image belongs to which data point.
